---
title: "math4800 project an R packing for distribution sampling"
author: "Bayard Rucker"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
--

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(math4800)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:


## General description

this R packaged allows you to perform rejection sampling from pdf and joint pdf. the user has to give an input pdf and specify the size of the sample they would like as well as bounds and the the maximum of the pdf 

## Rejection Sampling

  Rejection sampling is a type of exact simulation algorithem that works for all real numbers and in higher
  deminsions 
  
  algorithem steps
  1. selecte a random proposed candiate from a uniforma rv
  2. put the propsed candiate into the given pdf
  3. selecte your check value from a uniform between 0 and the maximum with in this case is C 
  4. compare if the output of the pdf and the original value is less than the check value then you accept it. 
  
  the is definder as rejectionSampler(n, pdf, lower, upper, C)
```{r}
      rejectionSampler(10,mypdf,0,1,1 )
      mypdf <- function(x){
         if( x <= 2  && x >= 0) {
            x/2
      }else{
            0
      }
    }
      


```
  



## Figures






The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
