---
title: "math4800 project an R packing for distribution sampling"
author: "Bayard Rucker"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
--

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(math4800)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:


## General description

this R packaged allows you to perform rejection sampling from pdf and joint pdf. the user has to give an input pdf and specify the size of the sample they would like as well as bounds and the the maximum of the pdf 

## Rejection Sampling

  Rejection sampling is a type of exact simulation algorithem that works for all real numbers and in higher
  deminsions 
  
  algorithem steps
  1. selecte a random proposed candiate from a uniforma rv
  2. put the propsed candiate into the given pdf
  3. selecte your check value from a uniform between 0 and the maximum with in this case is C 
  4. compare if the output of the pdf and the original value is less than the check value then you accept it. 
  
## simple rejction examples
  
  Here is a simple example of how the rejection sampler would run with a pdf from the package.
  this is a example if  you run rejection sampler with a small n and an example output
```{r}
          holder <- rejectionSampler(n = 5, pdf = mypdf, lower = 0, upper = 2, C = 1)
           hist(holder)
          # 0.01618789 0.24490906 0.05359767 0.49077322 1.70218396
          #pdf used in rejction ssampler
          mypdf <- function(x){
             if( x <= 2  && x >= 0) {
                x/2
             }else{
                 0
             }
          }
          
           holder1 <- rejectionSampler(n = 5, pdf = normpdf, lower = 0, upper = 3, C = 1)
          hist(holder1)
          # 2.2596883 0.9969329 0.8917946 1.2306571 1.4431262
           #pdf used in rejction ssampler
         normpdf <- function(x){
              dnorm(x)
          }

```
  


## 2D rejection sampler

  this rejection sampler works on join distributions that are defined on a square. the underlying algorithem works the same way expect 
  that here we are dealing with joint distributions that are defined for a specific region of the plain


  Here is a simpler joint rejection smapler with a joint normal distirbtion
```{r}
    holder <- jointRejectionSampler(n = 10, jointpdf = jointnorm, lower = 0, upper = 1, C = 1)
     hist(holder)
     # jointpdf used in rejction ssampler
    jointnorm <- function(x,y){
      if( x == y) {
        if(x >=0 && x <= 1 && y >= 0 && y <= 1) {
          joint <- dnorm(x) * dnorm(y)
        }else{
          0
        }
      }else{
        0
      }
    }
    
```
out put from the rejction sampler  
         x         y
1  0.3267715 0.8545568
2  0.7263313 0.4751195
3  0.6225835 0.4948918
4  0.5576389 0.2399189
5  0.4323270 0.8654610
6  0.3047128 0.8800500
7  0.2844174 0.8304783
8  0.6518205 0.6154928
9  0.5631891 0.4660881
10 0.3482138 0.4825210

    Another example with a joint uniform function 
```{r}
    holder <- jointRejectionSampler(n = 1000, jointpdf = jointunif, lower = 0, upper = 1, C = 1)
    hist(holder)
    # jointpdf used in rejction ssampler
    jointunif <- function(x,y){
       if(0 <= x && x <= 1 && 0 <= y && y <= 1) {
          .5
      }else {
          0
      }

    }
    
```
out put of the 2D rejection sampler using a joint uniform R.V.
            x          y
1  0.43593755 0.70838476
2  0.09677250 0.96729673
3  0.13023959 0.33197155
4  0.05804621 0.56934939
5  0.85796676 0.91361058
6  0.73084249 0.47628922
7  0.85954057 0.24595708
8  0.15807758 0.03623352
9  0.33162128 0.24503933
10 0.15412658 0.26729462








